---
title: "Theoretical (neutral)"
format: html
---

```{r setup}

library(untb)
library(dplyr)
library(ggplot2)

```

(January 10, 2023) After looking at a few different dimensions of the empirical side of this question (MACDB, Portal rodents, and the Portal plant timeseries), my sense is that there is not a clear and widespread signal in those data of the manipulated treatment consistently deviating from METE/FS more strongly than the control treatment. 

But I have a question about how this behaves on the theoretical side. Do deviations from METE/FS correspond to, for example, trajectory/stability of a neutral simulation?

Let's give that a shot.

### Code up neutral simulation in R

```{r}

untb_sim <- untb(start = rep(1, 100), prob = 0.01, gens = 5000, keep = T)

timestep_count <- function(sim_row) {
  
  simcount <- as.count(sim_row)
  count_df <- data.frame(
    species = names(simcount),
    abund = as.numeric(simcount))
  
  
}

untb_counts <- apply(untb_sim, MARGIN = 1, FUN = timestep_count, simplify = F)

untb_counts <- bind_rows(untb_counts, .id = "timestep")

```

### Calculate, for each timestep, deviation from METE and FS

### Plot deviation from METE and FS